---
title: "Datascience"
format: html
editor: visual
---

## 1. Answer the questions:

*What do you think being a data scientist is about*

-   Provide data-driven solutions for research and business

-   Utilize data to find answers and insights

*What differences/similarities do you see between data scientists and statisticians?*

-   Both rely on statistical thinking and data analysis

-   Data scientists more focused on data management, build models and write code, it aims to create practical, data-driven solutions

-   Statistician Focus more on theory and statistical algorithms

*How do you view yourself in relation to these two areas?*

-   I see myself as a data scientist, I enjoy applying my knowledge to provide data driven real-world solution to people

## 2. Adding R code chunks

Creating a density object from the dataset:

```{r}
y <- density(iris$Petal.Width)
```

*The class, type, and structure of the object y:*

```{r}
class(y)
typeof(y)
str(y)
```

Plot y:

```{r}
#| echo: false
plot(y, main = "Density of Petal Width in Iris Dataset")
```
